\documentclass[oneside,a4paper,11pt,explicit]{book}
\usepackage[utf8]{inputenc}
\usepackage{../common/kultem}
\usepackage[english]{babel}

%% INSERT YOUR PACKAGES HERE
\usepackage[accsupp]{axessibility}  % improves PDF readability for those with disabilities.
\usepackage[hidelinks]{hyperref}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{neuralnetwork}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usetikzlibrary{arrows.meta, positioning, calc, decorations.pathreplacing, shapes.geometric, fit}
\usepackage{amsmath,amssymb}
\usepackage{tcolorbox}
\tcbuselibrary{skins,breakable}
\newtcolorbox{insightbox}[1][]{
    colback=blue!3, colframe=blue!40!black, fonttitle=\bfseries,
    title={Theoretical Insight}, #1
}

% Python typesetting
\usepackage{listings}
\lstset{language=Python,basicstyle=\ttm}

\hypersetup{
	colorlinks=true,
	linkcolor=cyan,
	filecolor=magenta,
	urlcolor=cyan,
}
\usepackage{wrapfig}
\usepackage[giveninits=true,sorting=none]{biblatex} %Imports biblatex package
\addbibresource{references.bib} %Import the bibliography file

% Custom commands used later
\newcommand{\ANNta}[2]{% 1: TA name ; 2: TA mail
	\href{mailto:#2}{\color{black}{#1}}%
}
\newcommand{\ANNsession}[1]{% 1: Session number
	\title{\ANNtitle}
	\subtitle{\ANNsubtitle{#1}}
	\author{\ANNprof}
	\assistants{\ANNtas{}}
	\date{\ANNyear{}}
	\setcounter{chapter}{#1}
	\addtocounter{chapter}{-1}
}
\newcommand{\ANNtopic}[1]{% 1: Session topic
	\maketitle%
	\chapter{#1}%
}

% General configuration, shared across sessions
\newcommand{\ANNtitle}{Artificial Neural Networks \& Deep Learning}
\newcommand{\ANNsubtitle}[1]{Exercise Session #1}
\newcommand{\ANNprof}{Prof. Dr. ir. Johan A. K. Suykens}
\newcommand{\ANNtas}{%
	\ANNta{Sonny Achten}{sonny.achten@kuleuven.be}\\ %
	% \ANNta{Bram De Cooman}{bram.decooman@kuleuven.be}\\ %
	\ANNta{Maung Thant}{thant.maung@student.kuleuven.be}\\ %
	\ANNta{Xinjie Zeng}{xzeng@esat.kuleuven.be}%
}
\newcommand{\ANNyear}{2024-2025}

\addto\captionsenglish{\renewcommand{\chaptername}{Session}}


\ANNsession{2}

\begin{document}

\ANNtopic{Recurrent Neural Networks}

\kulbox{{\noindent{\bf Note:}
There is no need to repeat the information provided during the guided session.
Answer the questions as concise and accurate as possible.
Show your understanding of the concepts and methods by linking your observations to the theory.
Use graphical and/or tabular presentations where needed.
The \textit{page limit} for this exercise is \textit{4 printed pages}, including figures.}}

This assignment focuses on recurrent neural networks and their applications as associative memory for pattern denoising or recognition, and as nonlinear autoregressive models for time-series prediction. 
For the former application, we study the Hopfield network, which is tested on a dataset of noisy handwritten digits.
The latter application is demonstrated on a dataset of chaotic laser data, where we use multi-layer perceptrons and long short-term memory networks to predict the continuation of the time series.

\input{hopfield}

\input{timeseries}

\section*{References}
\printbibliography[heading=none]

\end{document}
